\begin{thebibliography}{30}
\label{sec:references}

\bibitem{Hewett:2012ns} 
  J.~L.~Hewett, H.~Weerts, R.~Brock, J.~N.~Butler, B.~C.~K.~Casey, J.~Collar, A.~de Gouvea and R.~Essig {\it et al.},
  ``Fundamental Physics at the Intensity Frontier,''
  arXiv:1205.2671 [hep-ex] (2012).

\bibitem{Wu:1957} C.~S.~Wu, E.~Ambler, R.~W.~Hayward, D.~D.~Hoppes, and R.~P.~Hudson, 
``Experimental Test of Parity Conservation in Beta Decay," 
Phys. Rev. 105, 1413 (1957).

\bibitem{LSCCQE} C.~H.~Llewellyn~Smith, 
``Neutrino Reactions at Accelerator Energies,"
Phys. Rep. 3C, 261 (1972).

\bibitem{MBCCQE} A.A.~Aguilar-Arevalo {\it et al.}, 
``First Measurement of the Muon Neutrino Charged Current Quasielastic Double Differential Cross section",
Phys. Rev. D81, 092005 (2010).

\bibitem{RS1pi} D.~Rein and L.~H.~Sehgal,
``Neutrino-Excitation of Baryon Resonances and Single Pion Production,"
 Annals of Physics 133, 79 (1981).

\bibitem{FKR} M.~Kislinger, R.~P.~Feynman and F.~Ravndal,
``Current Matrix Elements from a Relativistic Quark Model,"
 Phys. Rev. D3, 2706 (1971).

\bibitem{GKbook} C.~Giunti and C.~Kim,
``Fundamentals of Neutrino Physics and Astrophysics,"
Oxford Univ. Press (2007).

\bibitem{QPM} R.P.~Feynman, 
``Very high-energy collision of hadrons,"
 Phys. Rev. Lett. 23, 1415 (1969).

\bibitem{RFG} R.A.~Smith and E.J.~Moniz,
``Neutrino Reactions on Nuclear Targets,"
Nucl. Phys. B43, 605 (1972).

\bibitem{SF} H.~Nakamura and R.~Seki,
``Quasi-elastic Neutrino-Nucleus Scattering and Spectral Function,"
Nucl. Phys. B(Proc. Suppl.) 112, 197 (2002).

\bibitem{nueApp1} K.~Abe {\it et al.}  [T2K Collaboration],
  ``Indication of Electron Neutrino Appearance from an Accelerator-produced Off-axis Muon Neutrino Beam,"
  Phys.\ Rev.\ Lett.\ 107, 041801 (2011).

\bibitem{nueApp2}  K.~Abe {\it et al.}  [T2K Collaboration],
  ``Evidence of Electron Neutrino Appearance in a Muon Neutrino Beam,"
  Phys.\ Rev.\ D {\bf 88}, no. 3, 032002 (2013).

\bibitem{nueApp3} K.~Abe {\it et al.}  [T2K Collaboration],
 ``Observation of Electron Neutrino Appearance in a Muon Neutrino Beam,"
  Phys.\ Rev.\ Lett.\  112, 061802 (2014).

\bibitem{muDis} K.~Abe {\it et al.}  [T2K Collaboration],
  ``Measurement of Neutrino Oscillation Parameters from Muon Neutrino Disappearance with an Off-axis Beam,"
  Phys.\ Rev.\ Lett.\  111, no. 21, 211803 (2013).

\bibitem{ccinc} K.~Abe {\it et al.}  [T2K Collaboration],
 ``Measurement of the inclusive $\nu_\mu$ charged current cross section on carbon in the near detector of the T2K experiment,"
  Phys.\ Rev.\ D87, no. 9, 092003 (2013).

\bibitem{t2kex} K.~Abe {\it et al.}  [T2K Collaboration],
 ``The T2K Experiment,"
  Nucl.\ Instrum.\ Meth.\ A659, 106 (2011)

\bibitem{p0dnim} S.~Assylbekov {\it et al.},
``The T2K ND280 Off-Axis Pi-Zero Detector,"
 Nucl.\ Instrum.\  Meth.\ A686, 48 (2012).

\bibitem{fluxpred} K.~Abe {\it et al.}  [T2K Collaboration],
  \emph{T2K neutrino flux prediction},
  Phys.\ Rev.\ D87, no. 1, 012001 (2013)

\bibitem{fluxtn} N.~Abgrall {\it et al.}, 
``Flux Prediction and Uncertainties for the 2012a Oscillation Analysis,"
T2K Technical Note 99 (2013).

\bibitem{allabyref} J.~V.~Allaby {\it et al.},
``High-energy particle spectra from proton interactions at 19.2 GeV/c,"
Technical Report 70-12, CERN (1970).

\bibitem{eichtenref} T. Eichten {\it et al.},
``Particle production in proton interactions in nuclei at 24 GeV/c,"
Nucl. Phys. B44 (1972).

\bibitem{neut}  Y.~Hayato,
  ``A neutrino interaction simulation program library NEUT,''
  Acta Phys.\ Polon.\ B40, 2477 (2009).

\bibitem{xsectn}  P.~de~Perio {\it et al},
``Cross section parameters for the 2012a oscillation analysis,"
T2K Technical Note 108 (2013).

\bibitem{GRV98} 
  M.~Gluck, E.~Reya and A.~Vogt,
  ``Dynamical parton distributions revisited,''
  Eur.\ Phys.\ J.\ C5, 461 (1998).

\bibitem{ccminos} 
  P.~Adamson {\it et al.}  [MINOS Collaboration],
  ``Neutrino and Antineutrino Inclusive Charged-current Cross Section Measurements with the MINOS Near Detector,''
  Phys.\ Rev.\ D81, 072002 (2010)
  
\bibitem{recontn} A.~Hillairet {\it et al.},
``ND280 Reconstruction,"
T2K Technical Note 72 (2011).

\bibitem{p0dgeomtn} K.~Gilje,
``Geometry and Mass of the $\pi^0$ Detector in the ND280 Basket,"
T2K Technical Note 73 (2012).

\bibitem{fidmasstn} K.~Connoly {\it et al.},
``P0D Target Water Mass Calculation,"
T2K Technical Note 82 (2013).

\bibitem{chol} ``Cholesky Decomposition," in Wikipedia. Retrieved July 30, 2015 from \url{https://en.wikipedia.org/wiki/Cholesky_decomposition}.

\bibitem{smrdtn} O.~Perevozchikov,
``Magnet induced background for neutrino interactions and CC analysis in SMRD,"
T2K Technical Note 88 (2011).

\bibitem{tn80} T.~Campbell {\it et al.},
``Analysis of $\nu_\mu$ Charged Current Inclusive Events in the P0D in Runs 1+2+3+4,"
T2K Technical Note 80 (2014).

\bibitem{bayes}
M. Paterno, ``Calculating Efficiencies and Their Uncertainties," \url{http://home.fnal.gov/~paterno/images/effic.pdf}.

\bibitem{trkefftn} A.~Hillairet {\t et al.},
``ND280 tracker tracking efficiency,"
T2K Technical Note 75 (2015).

\bibitem{chmisidtn} J.~Caravaca {\it et al.},
``Charge Misidentification in local and global reconstruction,"
T2K Technical Note 48 (2011).

\end{thebibliography}